Robust Co-occurrence Quantification for Lexical Distributional Semantics

### 2016-06-10 paper.tex
Final changes

To answer these questions, we perform a systematic study of distributional models with a rich set of parameters on SimLex-999  \cite{hill2014simlex}, a lexical \emph{similairty} dataset, and test selected models on MEN \cite{Bruni:2014:MDS:2655713.2655714}, a lexical \emph{relatedness} dataset. The reason for choosing these is that they are currently widely used and surpass datasets stemming from information retrieval, WordSim-353 \cite{2002:PSC:503104.503110}, and computational linguistics, RG65 \cite{Rubenstein:1965:CCS:365628.365657}, in quantity by having more entries and in quality by attention to evaluated relations.

>>>>

To answer these questions, we perform a systematic study of distributional models with a rich set of parameters on SimLex-999  \cite{hill2014simlex}, a lexical \emph{similairty} dataset, and test selected models on MEN \cite{Bruni:2014:MDS:2655713.2655714}, a lexical \emph{relatedness} dataset. These datasets are currently widely used and surpass datasets stemming from information retrieval, WordSim-353 \cite{2002:PSC:503104.503110}, and computational linguistics, RG65 \cite{Rubenstein:1965:CCS:365628.365657}, in quantity by having more entries and in quality by attention to evaluated relations \cite{DBLP:journals/corr/MilajevsG16}.
